---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WRFutil

<!-- badges: start -->
<!-- badges: end -->

Some R utilities to work with WRF outputdata.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(WRFutil)
## basic example code
```

Whats implemented so far?

  * Read Temperature and calc temperature
  * Read Wind and recalc on sinus/cosinus alpha
    * Rotation is still missing
  * f_melt for ggplot
    * Not as fast as `reshape2::melt`, might go onto cpp?
  * Find a position in the grid by latitude and latitude
    * Needs to be reimplemented with a function refering to the file, not the already read lan/lot arrays

What else is missing?

  * Some form of georeferencing
  * Maybe a tool to create a static_drivöör?
  

```{r cars}
summary(cars)
```
